Data Management for LSST Special Programs

### 2023-10-19 sec_proc.tex
add footnote

\item \textbf{Short exposures --}
Special Programs that use short exposures would be limited to the
minimum exposure time is 1 second (stretch goal: 0.1 seconds).
There is a potential hardware boundary that limits the readout rate to 1 
every 15 seconds, which would affect the image acquisition rate and 
increase the overheads on short exposures.

>>>>

\item \textbf{Short exposures --}
Special Programs that use short exposures would be limited to the
minimum exposure time is 1 second (stretch goal: 0.1 seconds\footnote{A short-exposure survey 
of the bright stars of M67, described in Chapter 10.4 of the 
Observing Strategy White Paper \citep{2017arXiv170804058L}, suggests using the stretch goal of 
0.1 second exposures or, if that is not possible, \textit{"custom pixel masks to accurately perform 
photometry on stars as much as 6 magnitudes brighter than the saturation level"}. 
This may require User-Generated Processing.}).
There is a potential hardware boundary that limits the readout rate to 1 
every 15 seconds, which would affect the image acquisition rate and 
increase the overheads on short exposures.
